Optimization of the Walking Compass Gait Robot With the Use of Control Co-Design

### 2024-05-15 R0_journal/main.tex
...

\begin{document}

\maketitle{}

\begin{abstract}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=10cm]{./figures/onecycle.pdf}
\caption{One walking limit cycle of the compass gait. The swing leg makes a large swing (shown in blue, a large cicle) around while the stance leg only pivots (shown in orange.)}
\label{fig:onecycle}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=9cm]{./figures/states_onecycle.pdf}
\caption{States of the compas gait over time for one walking cycle.}
\label{fig:states_onecycle}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=10cm]{./figures/unstable_onecycle.pdf}
\caption{An example of an unstable limit cycle. In this case, the initial angular velocities make it impossible for the compass gait to start a walking cycle.}
\label{fig:unstable_onecycle}
\end{figure}

@@

\begin{equation}
\begin{aligned}
\text{Objective: Maximize $m_H$}\\
\text{Subject to:}\\
\text{Dynamic Constraints of System}\\
\text{Design Variables: 0.1$<$a$<$1, 0.1$<$b$<$1, (m)}\\
\text{Hip Mass: 5$<$$m_H$$<$80, (kg)}\\
\text{Leg Mass: } m = 5(a+b), \text{(kg)}\\
\text{End States $x_1$ and $x_2$ are Constrained Based on Trajectory Generation}
\end{aligned}
\label{eq:optprobsetup}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\text{Minimize: } J = \int_{0}^{t} (\tau / \tau_r)^2 + (t/t_r) \,dt \\
\text{Subject to:}\\
\text{Dynamic Constraints of System}\\
\text{Design Variables: } 0.1<a<1 (m), 0.1<b<1 (m), 0<m_H<100 \text{kg}\\
\text{Leg Mass: } m = 5(a+b)\\
\text{End States of $x_1$ and $x_2$ Constrained by Trajectory Generation}
\end{aligned}
\label{eq:OLprob}
\end{equation}

@@

Shown in this appendix is a more complete version of the dynamics equations of the compass gait. The swing stage dynamics can be written in standard planar manipulator 
dynamics form, shown in \ref{eq:swingeq}. The $\mb{M}$, $\mb{N}$, $\mb{G}$, and $\mb{U2}$ matrices are also shown in \ref{eq:M}, \ref{eq:N}, \ref{eq:G}, and \ref{eq:U} respectively.

@@

The transition equations when heel strike occurs are shown in \ref{eq:transeqn} and \ref{eq:transeqn2}, where $x^+$ signifies a state variables after heel strike and $x^-$ 
signals a state variable before
heel strike. The transition matrices $\mb{Q^+}$ and $\mb{Q^-}$ are shown in \ref{eq:Q-} and \ref{}. Note that $\alpha$ represents half the angle between the swing and stance 
legs.

@@

\bibliography{bib/references}
\bibliographystyle{plain}

>>>>

\begin{document}
\maketitle{}
\bibliographystyle{ieeetr}
\begin{abstract}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=6.5cm]{./figures/onecycle.pdf}
\caption{One walking limit cycle of the compass gait. The swing leg makes a large swing (shown in blue, a large cicle) around while the stance leg only pivots (shown in orange.)}
\label{fig:onecycle}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=8cm]{./figures/states_onecycle.pdf}
\caption{States of the compas gait over time for one walking cycle.}
\label{fig:states_onecycle}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=8cm]{./figures/unstable_onecycle.pdf}
\caption{An example of an unstable limit cycle. In this case, the initial angular velocities make it impossible for the compass gait to start a walking cycle.}
\label{fig:unstable_onecycle}
\end{figure}

@@

\begin{equation}
\begin{aligned}
&\text{Objective: Maximize $m_H$}\\
&\text{Subject to:}\\
&\text{Dynamic Constraints of System}\\
&\text{Design Variables: 0.1$<$a$<$1, 0.1$<$b$<$1, (m)}\\
&\text{Hip Mass: 5$<$$m_H$$<$80, (kg)}\\
&\text{Leg Mass: } m = 5(a+b), \text{(kg)}\\
&\text{End States $x_1$ and $x_2$ are Constrained by Trajectory Generation}
\end{aligned}
\label{eq:optprobsetup}
\end{equation}

@@

\begin{equation}
\begin{aligned}
&\text{Minimize: } J = \int_{0}^{t} (\tau / \tau_r)^2 + (t/t_r) \,dt \\
&\text{Subject to:}\\
&\text{Dynamic Constraints of System}\\
&\text{Design Variables: } 0.1<a<1 (m), 0.1<b<1 (m), 0<m_H<100 \text{kg}\\
&\text{Leg Mass: } m = 5(a+b)\\
&\text{End States of $x_1$ and $x_2$ Constrained by Trajectory Generation}
\end{aligned}
\label{eq:OLprob}
\end{equation}

@@

Shown in this appendix is a more complete version of the dynamics equations of the compass gait. The swing stage dynamics can be written in standard planar manipulator 
dynamics form, shown in \ref{eq:swingeq}. The $\mb{M}$, $\mb{N}$, $\mb{G}$, and $\mb{U}$ matrices are also shown in \ref{eq:M}, \ref{eq:N}, \ref{eq:G}, and \ref{eq:U2} respectively.

@@

The transition equations when heel strike occurs are shown in \ref{eq:transeqn} and \ref{eq:transeqn2}, where $x^+$ signifies a state variables after heel strike and $x^-$ 
signals a state variable before
heel strike. The transition matrices $\mb{Q^-}$ and $\mb{Q^+}$ are shown in \ref{eq:Q-} and \ref{eq:Q+}. Note that $\alpha$ represents half the angle between the swing and stance 
legs.

@@

\section*{Acknowledgement}
\LARGE
I would like to thank my professor, Sicheng He, who made this project possible. The knowledge and support he provided 
helped guide me through this project. I would also like to thank Shugo Kaneko for the help he provided by debugging my Dymos code which 
signficantly sped up the process of developing the simulation of the compass gait.

\pagestyle{plain}
\normalsize
\bibliography{bib/references}
